---
title: "APC_Paper Figs"
date: "6/13/2020"
output: pdf_document

author: |
  | Author 1^[Corresponding author: embruna@ufl.edu] $^1$,$^2$, Author 2 $^1$, Author 3 $^2$
  | $^1$WEC,  $^2$LAS


abstract: |
  Your abstract goes here...

<!-- bibliography: Path to your .bib file -->
<!-- csl: Path to your .csl file #sets the style of your bibliography -->

fig_caption: yes

always_allow_html: yes

# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage{endfloat}   
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary Stats

```{r njournals, echo=FALSE, message=FALSE}
library(tidyverse)
AllData<-read_csv(file="./data_clean/AllData.csv")
n_journals <- AllData %>% 
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(Journal))
tot_njournals<-sum(n_journals[2])
```
Total Journals: `r tot_njournals`.

```{r npapers, echo=FALSE, message=FALSE}
NumbArticles_JrnlType <- AllData %>% #number of papers per journal
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(DOI))
```
Total Articles - Paywall: `r NumbArticles_JrnlType[2,2]`

Total Articles - Open Access: `r NumbArticles_JrnlType[1,2]`


```{r ncountries,echo=FALSE, message=FALSE}
counrtriesOA1<-AllData %>% 
  filter(AuthorNum==1&JrnlType=="OA") %>% 
  group_by(Code) %>% 
  select(Code,IncomeGroup,Region) %>% 
  slice(1)

ncounrtriesOA1<-ungroup(counrtriesOA1) %>% 
  tally(n_distinct(Code))

counrtriesPW1<-AllData %>% 
  filter(AuthorNum==1&JrnlType=="PW") %>% 
  group_by(Code) %>% 
  select(Code,IncomeGroup,Region) %>% 
  slice(1)

ncounrtriesPW1<-ungroup(counrtriesPW1) %>% 
  tally(n_distinct(Code))




```
Number of Countries in PW journals (First Authors): `r ncounrtriesPW1`

Number of Countries in OA journals (First Authors): `r ncounrtriesOA1`



```{r bootstrapping, echo=FALSE, message=FALSE}
# source("./Rscript/functions/SubSamplePWvsOA_comparison.R")
# SubsampledPW.results_First<-SubSamplePWvsOA_comparison(AllData,"author_first")
# source("./Rscript/functions/SubSamplePWvsOA_comparison.R")
# SubsampledPW.results_Last<-SubSamplePWvsOA_comparison(AllData,"author_last")
# source("./Rscript/functions/SubSamplePWvsOA_comparison.R")
# SubsampledPW.results_All<-SubSamplePWvsOA_comparison(AllData,"author_all")
# source("./Rscript/functions/SubSamplePWvsOA_comparison.R")
# SubsampledPW.results_First_NOUSACHN<-SubSamplePWvsOA_comparison(AllData_noUSAorCHN,"author_first")
# source("./Rscript/functions/SubSamplePWvsOA_comparison.R")
# SubsampledPW.results_Last_NOUSACHN<-SubSamplePWvsOA_comparison(AllData_noUSAorCHN,"author_last")
# source("./Rscript/functions/SubSamplePWvsOA_comparison.R")
# SubsampledPW.results_All_NOUSACHN<-SubSamplePWvsOA_comparison(AllData_noUSAorCHN,"author_all")
```
## Table1
```{r Table1,echo=FALSE, message=FALSE}
library(tidyverse)
library(kableExtra)
AllData<-read_csv(file="./data_clean/AllData.csv")
AllData_noUSAorCHN<-read_csv(file="./data_clean/AllData_noUSAorCHN.csv")
source("./Rscript/functions/SummaryTable.R") 
Tables<-SummaryTable(AllData)
Table1<-Tables[2]
kable(head(Table1), digits = 2, format = "latex", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),full_width = F,
                font_size = 12,position = "left")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
