---
title: "APC Paper: Figures & Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document

# abstract: |
#   Text of abstract.
# 
# <!-- bibliography: Path to your .bib file -->
# <!-- csl: Path to your .csl file #sets the style of your bibliography -->

fig_caption: yes #yes will automatically add "Figure X" to the start 
# of the caption and reorders automatically if the figure position changes
always_allow_html: yes

# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage[disable,nofiglist, notablist]{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
# 
pdf_document:
extra_dependencies: "subfig"
appendix: 
- "Appendix.Rmd"  
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(readr)
```

```{r cached=TRUE}
knitr::opts_chunk$set(echo = FALSE)

MirrorPairs<-read.csv("./data_clean/MirrorPairs.csv")
WaiverCountries<-read.csv("./data_clean/WaiverCountries.csv")

AllData<-read_csv(file="./data_clean/all_data_analysis.csv")
AllData_missing<-AllData %>% 
  filter(AuthorNum==1) %>% 
  filter(is.na(First_Author_Country)) %>% 
  select(refID) 
AllData<-AllData %>% filter(!refID %in% AllData_missing$refID) 
rm(AllData_missing)

sole_author_pubs_ALL <-read_csv("./data_clean/one_author_pubs_ALL.csv")

coauthor_pubs_ALL<-read_csv("./data_clean/coauthor_pubs_ALL.csv")

sole_author_pubsNOCHNUSA_first_author<-read_csv("./data_clean/one_author_pubsNOCHNUSA.csv")

coauthor_pubsNOCHNUSA_first_author<-read_csv("./data_clean/coauthor_pubsNOCHNUSA.csv")

sole_author_pubs_ALL_first_author<-read_csv("./data_clean/sole_author_pubs_ALL_first_author.csv")

coauthor_pubs_ALL_first_author<-read_csv("./data_clean/coauthor_pubs_ALL_first_author.csv")

bootstrap_results<-read_csv('./output/bootstrap_results.csv')

bootstrap_results_countries<-read_csv("./output/bootstrap_results_countries.csv")

Table2.2<-read.csv('./output/Table2.2.csv')


```

### Summary Stats

```{r apcstats}
APC<-MirrorPairs %>% 
  filter(JrnlType=="OA") %>% 
  summarize(medianAPC=median(APC),
            avg_APC=mean(APC),
            sd_APC=sd(APC),
            maxAPC=max(APC),
            minAPC=min(APC))
APC_stats<-round(APC,2)
max<-APC_stats[4]
min<-APC_stats[5]
mean<-APC_stats[2]
sd<-APC_stats[3]
median<-APC_stats[1]
```
### APCs: 
* range: $`r min` - `r max`
* mean: $`r mean` +/- `r sd` SD
* median: $`r median`

```{r njournals}
n_journals <- AllData %>% 
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(Journal))
njournalsOA<-n_journals[1,2]
njournalsPW<-n_journals[2,2]

```
### Total Journals: OA N = `r njournalsOA`, PW N = `r njournalsPW`

```{r npapers, echo=FALSE,message = FALSE,warning=FALSE}
NumbArticles_JrnlType <- AllData %>% #number of papers per journal
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

NumbSoloArticles_JrnlType<-sole_author_pubs_ALL %>% 
group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

NumbCoAuthoredArticles_JrnlType<-coauthor_pubs_ALL %>% 
group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

n_OA<-NumbArticles_JrnlType[1,2]
n_PW<-NumbArticles_JrnlType[2,2]
Total_pubs<-n_OA+n_PW
```
### Total Number of Articles: N = `r Total_pubs`

### Articles in Paywall journals: N = `r NumbArticles_JrnlType[2,2]`

* single author: N = `r NumbSoloArticles_JrnlType[2,2]`

* Co-authored: N = `r NumbCoAuthoredArticles_JrnlType[2,2]`

### Articles in Open Access journals: N = `r NumbArticles_JrnlType[1,2]` 

* single author: N = `r NumbSoloArticles_JrnlType[1,2]`

* Co-authored: N = `r NumbCoAuthoredArticles_JrnlType[1,2]`


```{r ncountries, echo=FALSE,message = FALSE,warning=FALSE}
# Total Countries: sole-authored papers
n_countries_SOLE_authors<-sole_author_pubs_ALL_first_author %>% 
  summarize(n_distinct(Code))

# Total Countries: first authors of co-authored papers
n_countries_FIRST_authors<-coauthor_pubs_ALL_first_author %>% 
  summarize(n_distinct(Code))


countries_first_and_sole<-(c(sole_author_pubs_ALL_first_author$Code,
                                     coauthor_pubs_ALL_first_author$Code))

# Total Countries: all first authors (sole+first of authored)
n_countries_FIRST_AND_SOLE_authors<-n_distinct(countries_first_and_sole)

# Countries by Journal Type: Sole-authored papers                   
n_countries_SOLE_by_jrnl<-sole_author_pubs_ALL_first_author %>% 
  group_by(JrnlType) %>% 
  summarize(n_distinct(Code))
nSoleOA<-n_countries_SOLE_by_jrnl[1,2]
nSolePW<-n_countries_SOLE_by_jrnl[2,2]
# Countries by Journal Type: co-authored papers
n_countries_FIRST_by_jrnl<-coauthor_pubs_ALL_first_author %>% 
  group_by(JrnlType) %>% 
  summarize(n_distinct(Code))
nCoOA<-n_countries_FIRST_by_jrnl[1,2]
nCoPW<-n_countries_FIRST_by_jrnl[2,2]

# percent of articles with author in USA or CHN

n_articles_first_CHN_USA<-AllData %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="CHN"|Code=="USA") %>% 
  summarize(n_distinct(refID))

Perc_USA_orCHN<-round(n_articles_first_CHN_USA/Total_pubs*100,2)

n_articles_first_USA_OA<-AllData %>%
  filter(JrnlType=="OA") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="USA") %>% 
  summarize(n_distinct(refID))
Perc_USA_OA<-round(n_articles_first_USA_OA/NumbArticles_JrnlType[1,2]*100,2)

n_articles_first_CHN_OA<-AllData %>%
  filter(JrnlType=="OA") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="CHN") %>% 
  summarize(n_distinct(refID))
Perc_CHN_OA<-round(n_articles_first_CHN_OA/NumbArticles_JrnlType[1,2]*100,2)


n_articles_first_USA_PW<-AllData %>%
  filter(JrnlType=="PW") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="USA") %>% 
  summarize(n_distinct(refID))
Perc_USA_PW<-round(n_articles_first_USA_PW/NumbArticles_JrnlType[2,2]*100,2)

n_articles_first_CHN_PW<-AllData %>%
  filter(JrnlType=="PW") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="CHN") %>% 
  summarize(n_distinct(refID))

Perc_CHN_PW<-round(n_articles_first_CHN_PW/NumbArticles_JrnlType[2,2]*100,2)

```

#### No. of Countries: First Authors

#### By Author Category
* Overall (sole+first of coauthored): N = `r n_countries_FIRST_AND_SOLE_authors`
* Sole-authored papers N = `r n_countries_SOLE_authors` 
* First authors of co-authored papers N = `r n_countries_FIRST_authors` 

#### By Journal Type: 
* Sole authors OA: N = `r nSoleOA`
* Sole authors PW: N = `r nSolePW`
* First Author of coauthored papers OA: N = `r nCoOA`
* First Author of coauthored papers PW: N = `r nCoPW`

#### USA and CHN First Authors
* Percentage of Articles with USA or CHN first Author (overall): `r Perc_USA_orCHN` %

* Percentage of OA Articles with USA first Author: `r Perc_USA_OA[1,1]` %
* Percentage of OA Articles with CHN first Author: `r Perc_CHN_OA[1,1]` %

* Percentage of PW Articles with CHN first Author: `r Perc_CHN_PW[1,1]` %
* Percentage of PW Articles with USA first Author: `r Perc_USA_PW[1,1]` %



<!-- \newpage -->

<!-- ```{r child = "Smith_etal_FigsTables.Rmd"} -->
<!-- ``` -->
