---
title: "APC Paper: Figures & Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document

# abstract: |
#   Text of abstract.
# 
# <!-- bibliography: Path to your .bib file -->
# <!-- csl: Path to your .csl file #sets the style of your bibliography -->

fig_caption: yes #yes will automatically add "Figure X" to the start 
# of the caption and reorders automatically if the figure position changes
always_allow_html: yes

# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage[disable,nofiglist, notablist]{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
# 
pdf_document:
extra_dependencies: "subfig"
appendix: 
- "Appendix.Rmd"  
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(readr)
```

```{r cached=TRUE}
knitr::opts_chunk$set(echo = FALSE)

MirrorPairs<-read.csv("./data_clean/MirrorPairs.csv")
WaiverCountries<-read.csv("./data_clean/WaiverCountries.csv")

AllData<-read_csv(file="./data_clean/all_data_analysis.csv")
AllData_missing<-AllData %>% 
  filter(AuthorNum==1) %>% 
  filter(is.na(First_Author_Country)) %>% 
  select(refID) 
AllData<-AllData %>% filter(!refID %in% AllData_missing$refID) 
rm(AllData_missing)

sole_author_pubs_ALL <-read_csv("./data_clean/one_author_pubs_ALL.csv")

coauthor_pubs_ALL<-read_csv("./data_clean/coauthor_pubs_ALL.csv")

sole_author_pubsNOCHNUSA_first_author<-read_csv("./data_clean/one_author_pubsNOCHNUSA.csv")

coauthor_pubsNOCHNUSA_first_author<-read_csv("./data_clean/coauthor_pubsNOCHNUSA.csv")

sole_author_pubs_ALL_first_author<-read_csv("./data_clean/sole_author_pubs_ALL_first_author.csv")

coauthor_pubs_ALL_first_author<-read_csv("./data_clean/coauthor_pubs_ALL_first_author.csv")

bootstrap_results<-read_csv('./output/bootstrap_results.csv')

bootstrap_results_countries<-read_csv("./output/bootstrap_results_countries.csv")

Table2.2<-read.csv('./output/Table2.2.csv')


```

### Summary Stats

```{r apcstats}
APC<-MirrorPairs %>% 
  filter(JrnlType=="OA") %>% 
  summarize(medianAPC=median(APC),
            avg_APC=mean(APC),
            sd_APC=sd(APC),
            maxAPC=max(APC),
            minAPC=min(APC))
APC_stats<-round(APC,2)
max<-APC_stats[4]
min<-APC_stats[5]
mean<-APC_stats[2]
sd<-APC_stats[3]
median<-APC_stats[1]
```
### APCs: 
* range: $`r min` - `r max`
* mean: $`r mean` +/- `r sd` SD
* median: $`r median`

```{r njournals}
n_journals <- AllData %>% 
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(Journal))
njournalsOA<-n_journals[1,2]
njournalsPW<-n_journals[2,2]

```
### Total Journals: OA N = `r njournalsOA`, PW N = `r njournalsPW`

```{r npapers, echo=FALSE,message = FALSE,warning=FALSE}
NumbArticles_JrnlType <- AllData %>% #number of papers per journal
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

NumbSoloArticles_JrnlType<-sole_author_pubs_ALL %>% 
group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

NumbCoAuthoredArticles_JrnlType<-coauthor_pubs_ALL %>% 
group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

n_OA<-NumbArticles_JrnlType[1,2]
n_PW<-NumbArticles_JrnlType[2,2]
Total_pubs<-n_OA+n_PW
```
### Total Number of Articles: N = `r Total_pubs`

### Articles in Paywall journals: N = `r NumbArticles_JrnlType[2,2]`

* single author: N = `r NumbSoloArticles_JrnlType[2,2]`

* Co-authored: N = `r NumbCoAuthoredArticles_JrnlType[2,2]`

### Articles in Open Access journals: N = `r NumbArticles_JrnlType[1,2]` 

* single author: N = `r NumbSoloArticles_JrnlType[1,2]`

* Co-authored: N = `r NumbCoAuthoredArticles_JrnlType[1,2]`


```{r ncountries, echo=FALSE,message = FALSE,warning=FALSE}
# Total Countries: sole-authored papers
n_countries_SOLE_authors<-sole_author_pubs_ALL_first_author %>% 
  summarize(n_distinct(Code))

# Total Countries: first authors of co-authored papers
n_countries_FIRST_authors<-coauthor_pubs_ALL_first_author %>% 
  summarize(n_distinct(Code))


countries_first_and_sole<-(c(sole_author_pubs_ALL_first_author$Code,
                                     coauthor_pubs_ALL_first_author$Code))

# Total Countries: all first authors (sole+first of authored)
n_countries_FIRST_AND_SOLE_authors<-n_distinct(countries_first_and_sole)

# Countries by Journal Type: Sole-authored papers                   
n_countries_SOLE_by_jrnl<-sole_author_pubs_ALL_first_author %>% 
  group_by(JrnlType) %>% 
  summarize(n_distinct(Code))
nSoleOA<-n_countries_SOLE_by_jrnl[1,2]
nSolePW<-n_countries_SOLE_by_jrnl[2,2]
# Countries by Journal Type: co-authored papers
n_countries_FIRST_by_jrnl<-coauthor_pubs_ALL_first_author %>% 
  group_by(JrnlType) %>% 
  summarize(n_distinct(Code))
nCoOA<-n_countries_FIRST_by_jrnl[1,2]
nCoPW<-n_countries_FIRST_by_jrnl[2,2]

# percent of articles with author in USA or CHN

n_articles_first_CHN_USA<-AllData %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="CHN"|Code=="USA") %>% 
  summarize(n_distinct(refID))

Perc_USA_orCHN<-round(n_articles_first_CHN_USA/Total_pubs*100,2)

n_articles_first_USA_OA<-AllData %>%
  filter(JrnlType=="OA") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="USA") %>% 
  summarize(n_distinct(refID))
Perc_USA_OA<-round(n_articles_first_USA_OA/NumbArticles_JrnlType[1,2]*100,2)

n_articles_first_CHN_OA<-AllData %>%
  filter(JrnlType=="OA") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="CHN") %>% 
  summarize(n_distinct(refID))
Perc_CHN_OA<-round(n_articles_first_CHN_OA/NumbArticles_JrnlType[1,2]*100,2)


n_articles_first_USA_PW<-AllData %>%
  filter(JrnlType=="PW") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="USA") %>% 
  summarize(n_distinct(refID))
Perc_USA_PW<-round(n_articles_first_USA_PW/NumbArticles_JrnlType[2,2]*100,2)

n_articles_first_CHN_PW<-AllData %>%
  filter(JrnlType=="PW") %>% 
  filter(AuthorNum==1) %>% 
  filter(Code=="CHN") %>% 
  summarize(n_distinct(refID))

Perc_CHN_PW<-round(n_articles_first_CHN_PW/NumbArticles_JrnlType[2,2]*100,2)

```

#### No. of Countries: First Authors

#### By Author Category
* Overall (sole+first of coauthored): N = `r n_countries_FIRST_AND_SOLE_authors`
* Sole-authored papers N = `r n_countries_SOLE_authors` 
* First authors of co-authored papers N = `r n_countries_FIRST_authors` 

#### By Journal Type: 
* Sole authors OA: N = `r nSoleOA`
* Sole authors PW: N = `r nSolePW`
* First Author of coauthored papers OA: N = `r nCoOA`
* First Author of coauthored papers PW: N = `r nCoPW`

#### USA and CHN First Authors
* Percentage of Articles with USA or CHN first Author (overall): `r Perc_USA_orCHN` %

* Percentage of OA Articles with USA first Author: `r Perc_USA_OA[1,1]` %
* Percentage of OA Articles with CHN first Author: `r Perc_CHN_OA[1,1]` %

* Percentage of PW Articles with CHN first Author: `r Perc_CHN_PW[1,1]` %
* Percentage of PW Articles with USA first Author: `r Perc_USA_PW[1,1]` %

<!--chapter:end:Smith_et_al_SummaryStats.Rmd-->

---
title             : "**Article Processing Charges: Gateways or Gatekeepers of Author Diversity? OR Article Processing Charges alter the geographic representation of authors in Open Access journals**"
shorttitle        : "APCs and Author Diversity "

author: 
  - name          : "Audrey C. Smith"
    affiliation   : "1"
    role:         
      - Methodology
      - Investigation
      - Writing - Original Draft
      - Writing - Review & Editing
  - name          : "Leandra Merz"
    affiliation   : "1"
    role:
      - Methodology
      - Investigation
      - Writing - Original Draft
      - Writing - Review & Editing
  - name          : "Jesse Borden"
    affiliation   : "2"
    role:
      - Methodology
      - Investigation
      - Software
      - Writing - Review & Editing
  - name          : "Chris Gulick"
    affiliation   : "3"
    role:
      - Methodology
      - Investigation
      - Writing - Review & Editing
  - name          : "Akhil Kshirsagar"
    affiliation   : "1"
    role:
      - Methodology
      - Investigation
      - Writing - Review & Editing
  - name          : "Emilio M. Bruna"
    affiliation   : "3,4"
    corresponding : no    # Define only one corresponding author
    address       : "Center for Latin American Studies, University of Florida, PO Box 115530, Gainesville, Florida, 32611 USA"
    email         : "embruna@ufl.edu"
    role:
      - Conceptualization
      - Methodology
      - Data collection
      - Software
      - Data Curation
      - Writing - Original Draft
      - Writing - Review & Editing
      - Supervision

affiliation:
  - id            : "1"
    institution   : "Department of Geography, University of Florida"
  - id            : "2"
    institution   : "School for Natural Resources and the Environment, University of Florida"
  - id            : "3"
    institution   : "Department of Wildlife Ecology and Conservation, University of Florida"
  - id            : "4"
    institution   : "Center for Latin American Studies, University of Florida"

authornote: |
  A. Smith, Department of Geography, University of Florida, PO Box 117315, Gainesville, Florida, 32611 USA
  
  L. Merz, Department of Geography, University of Florida, PO Box 117315, Gainesville, Florida, 32611 USA
  
  A. Kshirsagar, Department of Geography, University of Florida, PO Box 117315, Gainesville, Florida, 32611 USA
  
  J. Borden, School for Natural Resources and the Environment, University of Florida, PO Box 116455, Gainesville, Florida, 32611 USA
  
  C. Gulick, Department of Wildlife Ecology and Conservation, University of Florida, PO Box 110430, Gainesville, Florida, 32611 USA
  
  E. M. Bruna, Department of Wildlife Ecology and Conservation, University of Florida, PO Box 110430, Gainesville, Florida, 32611 USA and Center for Latin American Studies, University of Florida, PO Box 115530, Gainesville, Florida, 32611 USA
  
  A. Smith and L. Merz are contributed equally to this manuscript.
  
  We thank N. Emery, C. Scott, and D. Forero for assistance in gathering preliminary data for the project and ---- for helpful discussions and feedback on the manuscript.

abstract: |
 To be added last.
  
keywords: "article processing charges, author diversity, Global South, geographic diversity, mirror journals, open access"

wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : "papaja::apa6_pdf"

---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")

library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(stringr)
library(kableExtra)
library(readr)
```



```{r analysis-preferences}
# # Seed for random number generation
# set.seed(42)
# knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

Content in Open Access (i.e., OA) journals can be read without payment or subscription, and the number of OA articles published annually has grown dramatically over the last two decades (Piwowar et al., 2018; Tennant et al., 2016). In addition to benefiting readers without access to traditional subscription journals (i.e., Paywall journals, PW), publishing in OA journals can also benefit an article’s authors (McKiernan et al., 2016; Tennant et al., 2016). For instance, articles in OA journals can garner more online views, have higher download rates, and accrue more citations over time than articles in PW outlets (Davis, 2011; Eysenbach, 2006; Wang et al., 2015). Metrics such as these are increasingly being taken into consideration when conducting performance evaluations of scientists, including the tenure and promotion process in academic institutions (Schimanski & Alperin, 2018). Publishing in OA journals can, therefore, play an important role in a scientist’s professional advancement and status. This is especially true if the OA journals have other characteristics used as indicators of prestige by evaluators, such as name recognition, high impact factors, perceived prestige, and association with major academic societies (Schimanski & Alperin, 2018). 



# Methods
$$D^2 = \frac{1}{\Sigma_{i-1}^R * p_i^2}$$


We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

<!-- \newpage -->
<!-- ```{r child = "Smith_etal_FigsTables.Rmd"} -->
<!-- ``` -->

\newpage
# Appendix
<!-- ```{r child = "Smith_etal_Appendix.Rmd"} -->
<!-- ``` -->

<!--chapter:end:Smith_etal_APC_ms.Rmd-->

---
title: "Smith et al. Appendices"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
fig_caption: FALSE #yes will automatically add "Figure X" to the start
# of the caption and reorders automatically if the figure position changes
always_allow_html: yes
# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage[nomarkers,nofiglist, notablist]{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(stringr)
library(kableExtra)
library(readr)
```

```{r laodsappendix, cached=TRUE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)

MirrorPairs<-read.csv("./data_clean/MirrorPairs.csv")
WaiverCountries<-read.csv("./data_clean/WaiverCountries.csv")

AllData<-read_csv(file="./data_clean/all_data_analysis.csv")
AllData_missing<-AllData %>%
  filter(AuthorNum==1) %>%
  filter(is.na(First_Author_Country)) %>%
  select(refID)
AllData<-AllData %>% filter(!refID %in% AllData_missing$refID)
rm(AllData_missing)

sole_author_pubs_ALL <-read_csv("./data_clean/one_author_pubs_ALL.csv")
coauthor_pubs_ALL<-read_csv("./data_clean/coauthor_pubs_ALL.csv")
sole_author_pubsNOCHNUSA_first_author<-read_csv("./data_clean/one_author_pubsNOCHNUSA.csv")
coauthor_pubsNOCHNUSA_first_author<-read_csv("./data_clean/coauthor_pubsNOCHNUSA.csv")
sole_author_pubs_ALL_first_author<-read_csv("./data_clean/sole_author_pubs_ALL_first_author.csv")
coauthor_pubs_ALL_first_author<-read_csv("./data_clean/coauthor_pubs_ALL_first_author.csv")
bootstrap_results<-read_csv('./output/bootstrap_results.csv')
bootstrap_results_countries<-read_csv("./output/bootstrap_results_countries.csv")
Table2.2<-read.csv('./output/Table2.2.csv')


```

```{r npapers_appendix, echo=FALSE,message = FALSE,warning=FALSE}
NumbArticles_JrnlType <- AllData %>% #number of papers per journal
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

NumbSoloArticles_JrnlType<-sole_author_pubs_ALL %>% 
group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

NumbCoAuthoredArticles_JrnlType<-coauthor_pubs_ALL %>% 
group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

n_OA<-NumbArticles_JrnlType[1,2]
n_PW<-NumbArticles_JrnlType[2,2]
Total_pubs<-n_OA+n_PW
```

```{r rich_div_figs1, echo=FALSE,message = FALSE,warning=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
insert_custom1<-n_OA
insert_custom2<-n_PW
```

```{r Appendix1,fig.align='center', fig.cap=paste("Author Geographic Diversity (Shannon Index) for N = ", insert_custom1, " Open Access articles (red bar) and 1000 identically sized collections of Paywalled articles selected by bootstrapping from a pool of ",insert_custom2, " articles.  The black line indicates the mean value for the 1000 bootstrap collections."),fig.fullwidth=TRUE}

source("./Rscript/functions_figures/DivBootFig_shannon.R")
DivBootFig_shannon(bootstrap_results)
```

```{r Appendix2,fig.align='center',fig.cap="Percentage of lead authors based in different countries. Includes both paywalled and open access journals; 'lead authors' are both the authors of sole-authored papers and first authors of co-authored papers."}
source("./Rscript/functions_figures/AppFig1.R") 
AppFig1(AllData)
```

```{r Appendix3, fig.align='center', fig.cap=paste("Geographic Evenness for N = ", insert_custom1, " Open Access articles (red bar) and 1000 identically sized collections of Paywalled articles selected by bootstrapping from a pool of ",insert_custom2, " articles. The black line indicates the mean value for the 1000 bootstrap collections."), fig.fullwidth=TRUE}
source("./Rscript/functions_figures/EvenFig.R") 
EvenFig(bootstrap_results)
```

```{r Appendix4, echo=FALSE,message = FALSE,warning=FALSE}
waiver_table<-read_csv(file="./data_clean/waiver_table.csv")
waiver_table<-waiver_table %>%
  select(WaiverGroup,IncomeGroup,Region,Country) %>%
  drop_na(WaiverGroup) 
waiver_table$group<-waiver_table$group<-NA
waiver_table<-waiver_table %>%
  group_by(WaiverGroup,IncomeGroup,Region) %>% 
  mutate(group = replace(group, row_number() <6, "1")) %>% 
  mutate(group = replace(group, (row_number() >5&row_number() <11), "2")) %>% 
  mutate(group = replace(group, (row_number() >10&row_number() <16), "3")) %>% 
  mutate(group = replace(group, (row_number() >15&row_number() <21), "4")) %>% 
  mutate(group = replace(group, (row_number() >20), "5")) %>% 
  # mutate(group = replace(group, row_number() >25, "6")) %>%  
  group_by(WaiverGroup,IncomeGroup,Region,group) %>% 
  summarize(CountryGroups = str_c(Country, collapse = ", ")) #this line takes the individual
#cells and collapses them into a single one
waiver_table$group<-NULL

waiver_table<-waiver_table %>% 
  group_by(WaiverGroup,IncomeGroup,Region) %>% 
  mutate(Region = replace(Region, row_number() > 1, "")) %>% 
  group_by(WaiverGroup,IncomeGroup) %>% 
  mutate(IncomeGroup = replace(IncomeGroup, row_number() > 1, "")) %>% 
  group_by(WaiverGroup) %>% 
  mutate(WaiverGroup = replace(WaiverGroup, row_number() > 1, "")) %>% 
  drop_na(CountryGroups)

waiver_table<-as.data.frame(waiver_table)

names(waiver_table)<-c("Elsevier Waiver Group","World Bank Income Group","World Bank Region", "Countries")



kable(waiver_table, 
      digits = 1, 
      format = "latex", 
      align="l",
      row.names = FALSE, 
      booktabs=T,
      linesep = "", 
      # longtable = TRUE,
      caption = "Countries eligible for Article Processing Charge waivers through Elsevier's 'Research4Life' program by World Bank Global Region and Income Group.") %>% kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down",
                                  "repeat_header"),
                full_width = F,
                font_size = 12,
                position = "left")
```

<!--chapter:end:Smith_etal_Appendix.Rmd-->

---
title: "APC Paper: Figures & Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document

# abstract: |
#   Text of abstract.
# 
# <!-- bibliography: Path to your .bib file -->
# <!-- csl: Path to your .csl file #sets the style of your bibliography -->

fig_caption: yes #yes will automatically add "Figure X" to the start 
# of the caption and reorders automatically if the figure position changes
always_allow_html: yes

# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage[nomarkers,nolists]{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
# 
pdf_document:
extra_dependencies: "subfig"
appendix: 
- "Appendix.Rmd"  
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(readr)
library(egg)
```

```{r cached=TRUE}
knitr::opts_chunk$set(echo = FALSE)

MirrorPairs<-read.csv("./data_clean/MirrorPairs.csv")
WaiverCountries<-read.csv("./data_clean/WaiverCountries.csv")



AllData<-read_csv(file="./data_clean/all_data_analysis.csv")
AllData_missing<-AllData %>% 
  filter(AuthorNum==1) %>% 
  filter(is.na(First_Author_Country)) %>% 
  select(refID) 
AllData<-AllData %>% filter(!refID %in% AllData_missing$refID) 
rm(AllData_missing)

sole_author_pubs_ALL <-read_csv("./data_clean/one_author_pubs_ALL.csv")

coauthor_pubs_ALL<-read_csv("./data_clean/coauthor_pubs_ALL.csv")

sole_author_pubsNOCHNUSA_first_author<-read_csv("./data_clean/one_author_pubsNOCHNUSA.csv")

coauthor_pubsNOCHNUSA_first_author<-read_csv("./data_clean/coauthor_pubsNOCHNUSA.csv")

sole_author_pubs_ALL_first_author<-read_csv("./data_clean/sole_author_pubs_ALL_first_author.csv")

coauthor_pubs_ALL_first_author<-read_csv("./data_clean/coauthor_pubs_ALL_first_author.csv")

bootstrap_results<-read_csv('./output/bootstrap_results.csv')

bootstrap_results_countries<-read_csv("./output/bootstrap_results_countries.csv")

Table2.2<-read.csv('./output/Table2.2.csv')


```

```{r npapers, echo=FALSE,message = FALSE,warning=FALSE}
NumbArticles_JrnlType <- AllData %>% #number of papers per journal
  group_by(JrnlType) %>% 
  summarize(n=n_distinct(refID))

n_OA<-NumbArticles_JrnlType[1,2]
n_PW<-NumbArticles_JrnlType[2,2]
Total_pubs<-n_OA+n_PW
```

```{r rich_div_figs1, echo=FALSE,message = FALSE,warning=FALSE}
knitr::opts_knit$set(eval.after = "fig.cap")
insert_custom1<-n_OA
insert_custom2<-n_PW
# Figure - Diversity
source("./Rscript/functions_figures/DivBootFig.R")
DivBootFig<-DivBootFig(bootstrap_results)
# Figure - Richness
source("./Rscript/functions_figures/RichBootFig.R")
RichBootFig<-RichBootFig(bootstrap_results)
```

```{r rich_div_figs, echo=FALSE,message = FALSE,warning=FALSE}
source("./Rscript/functions_figures/CountryPlot.R") 
p1<-CountryPlot(sole_author_pubs_ALL_first_author,"author_first","OA")
p2<-CountryPlot(sole_author_pubs_ALL_first_author,"author_first","PW")
p3<-CountryPlot(coauthor_pubs_ALL_first_author,"author_first","OA")
p4<-CountryPlot(coauthor_pubs_ALL_first_author,"author_first","PW")
```

```{r Fig1, fig.align='center',fig.cap="Percentage of authors of single-author publications in (A) Open Access journals and (B) Paywall journals based in different countries.",fig.height = 9,fig.width=6}
grid.arrange(p1, p2, ncol = 1)
```

```{r Fig2, fig.align='center',fig.cap="Percentage of first authors of co-authored publications in (A) Open Access journals and (B) Paywall journals that are based in different countries,",fig.height = 9,fig.width=6}
# coauthored, first author, OA
grid.arrange(p3, p4, ncol = 1)
```

```{r Fig3, fig.align='center', fig.cap=paste("Author Geographic Richness for N = ", insert_custom1, " Open Access articles (red bar) and 1000 identically sized collections of Paywalled articles selected by bootstrapping from a pool of ",insert_custom2, " articles. The black line indicates the mean value for the 1000 bootstrap collections."), fig.fullwidth=TRUE}
RichBootFig
```

```{r Fig4, fig.align='center', fig.cap=paste("Author Geographic Diversity (Inverse Simpson's Index) for N = ", insert_custom1, " Open Access articles (red bar) and 1000 identically sized collections of Paywalled articles selected by bootstrapping from a pool of ",insert_custom2, " articles.  The black line indicates the mean value for the 1000 bootstrap collections."),fig.fullwidth=TRUE}
DivBootFig
```

```{r Fig5, fig.align='center', fig.cap="Percentage of first authors of (A) co-authored and (B) sole-authored open access articles (red bars) and 1000 bootstrapped collections of paywalled articles that are based in different global regions.", fig.fullwidth=TRUE,fig.height = 24,fig.width=20}
source("./Rscript/functions_figures/IncomePlot.R") 
IncomePlot(bootstrap_results,bootstrap_results_countries,"All")
```

```{r Fig6, fig.align='center', fig.cap="Percentage of first authors of (A) co-authored and (B) sole-authored open access articles (red bars) and 1000 bootstrapped collections of paywalled articles that are based in different global regions.",fig.fullwidth=TRUE,fig.height = 24,fig.width=20}
source("./Rscript/functions_figures/RegionPlot.R") 
RegionPlot(bootstrap_results,bootstrap_results_countries,"All")
```


```{r Table1, echo=FALSE,message = FALSE,warning=FALSE}
source("./Rscript/functions/SummaryTable.R") 
Tables<-SummaryTable(AllData)
Table1<-Tables[2]
Table1<-as.data.frame(Table1)
names(Table1)<-c("Journal","Articles","Articles - OA Mirror","APC (US$)")
Table1[4,1]<-"BiochimieSuper1"
Table1[27,1]<-"Microelectronic EngineeringSuper2"
Table1[39,4]<-""

Table1<-arrange(Table1,desc(Table1[4]))

tmp<-knitr::kable(Table1, 
      digits = 2,
      align="c",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "The Elsevier subscription journals included in this study, the number of articles published in each journal dueing the focal period, the number of articles published in their respective open access mirror journals, and the article processing charge (APC) for each open access mirror journal.") %>%
  kable_styling(bootstrap_options = c("hover"),
                full_width = F,
                latex_options="scale_down",
                font_size = 12,
                position = "left") %>%
  footnote(number = c("OA Mirror title: Biochimie Open", "OA Mirror title: Micro and Nano Engineering"))
tmp<-str_replace(tmp, "Super1", "$^{1}$")
tmp<-str_replace(tmp, "Super2", "$^{2}$")
knitr::asis_output(tmp)
```

```{r Table2, echo=FALSE,message = FALSE,warning=FALSE}
SubsampledPW.results_Solo<-read_csv('output/SubsampledPW.results_RichDiv_SOLO_ALL.csv')
SubsampledPW.results_Solo_NoUSACHN<-read_csv('output/SubsampledPW.results_RichDiv_SOLO_ALL.csv')

probs<-read_csv("./output/probs.csv")

source("./Rscript/functions_figures/Table2.R")
Table2<-Table2(sole_author_pubs_ALL_first_author,
               sole_author_pubsNOCHNUSA_first_author,
               coauthor_pubs_ALL_first_author,
               coauthor_pubsNOCHNUSA_first_author)
Table2<-as.data.frame(Table2)
Table2<-bind_cols(Table2,probs)
Table2<-Table2 %>% select("Metric",
                          "Author",
                          "OA"="OA (All Countries)",
                          "Mean PW (All Countries)",
                          "all",
                          # "PW 95% CI (All Countries)",
                          "OA (USA & CHN excluded)",
                          # "PW 95% CI (USA & CHN excluded)",
                          "Mean PW (USA & CHN excluded)",
                          "without"
                          )


names(Table2)<-c("Metric",
                 "Author",
                 "OA",
                 paste("PW","(mean\u00B1SD)",sep=" "),
                 "Pr(PW>OA)",
                 # "PW 95% CI",
                 "OA",
                 # "PW 95% CI",
                 paste("PW","(mean\u00B1SD)",sep=" "),
                 "Pr(PW>OA)"
                 )

kable(Table2, 
      digits = 1, 
      format = "latex", 
      align="c",
      row.names = FALSE, 
      booktabs=T,
      linesep = "", 
      caption = "Geographic Richness and Geographic Diversity of lead authors of papers published in Open Access (OA) and Paywalled (PW) journals. Single: authors of sole-authored papers; First: first authors of co-authored papers.") %>% 
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = F,
                font_size = 12,
                position = "center") %>% 
  add_header_above(c(" " = 2, "All Countries" = 3, "Without China & USA" = 3))
```

```{r Table3, echo=FALSE,message = FALSE,warning=FALSE}
stipends<-read_csv(file="./data_clean/stipends.csv")
stipends<-as.data.frame(stipends)
stipends$agency<-c("CNPq","","CONACYT","","SERB","RISTEKDIKTI","NRF","")
source<-stipends$source
stipends<-stipends %>% select(country, degree, agency,stipend_USD)
names(stipends)<-c("Country","Degree","Agency","Stipend (US$)")
stipends[1,1]<-"BrazilSuper1"
stipends[2,1]<-""
stipends[3,1]<-"MexicoSuper2"
stipends[4,1]<-""
stipends[5,1]<-"IndiaSuper3"
stipends[6,1]<-"IndonesiaSuper4"
stipends[7,1]<-"South AfricaSuper5"
stipends[8,1]<-""
foot1<-source[1]
foot2<-source[3]
foot3<-source[5]
foot4<-source[6]
foot5<-source[7]
foot5<-"https://www.nrf.ac.za"
# foot4<-gsub("%20Scholarships%","%20Scholarships\n%",foot4)
# stipends[4]<-NULL
tmp<-knitr::kable(stipends,
                  digits = 1, 
                  format = "latex", 
                  align="c",
                  row.names = FALSE, 
                  booktabs=T,
                  linesep = "", 
                  caption = "Monthly stipends for graduate students in select countries") %>% 
  kable_styling(bootstrap_options = c("hover"),
                latex_options = c("scale_down"),
                full_width = T,
                font_size = 12,
                position = "center") %>% 
  footnote(number = c(foot1,foot2,foot3,foot4,foot5))
tmp<-str_replace(tmp, "Super1", "$^{1}$")
tmp<-str_replace(tmp, "Super2", "$^{2}$")
tmp<-str_replace(tmp, "Super3", "$^{3}$")
tmp<-str_replace(tmp, "Super4", "$^{4}$")
tmp<-str_replace(tmp, "Super5", "$^{5}$")
knitr::asis_output(tmp)

```

<!-- \newpage -->
<!-- # Appendix -->
<!-- ```{r child = "Smith_etal_Appendix.Rmd"} -->
<!-- ``` -->

<!--chapter:end:Smith_etal_FigsTables.Rmd-->

